
\section*{Initial planning}
\begin{itemize}
    \item \textcolor{blue}{In this part of the project, you are supposed to construct a new policy for making either treatment or vaccination decisions.}
        \begin{itemize}
            \item  
        \end{itemize}
    \item \textcolor{blue}{It is your choice which one of the two you wish to work on.}
    \item \textcolor{blue}{In either case, choose one and stick to it.}
    \item \textcolor{blue}{The policies will be ran with a simulator to be provided later.}
    \item \textcolor{blue}{No matter what you choose, be sure to define the utility that your policy should maximise.}
        \begin{itemize}
            \item 
        \end{itemize}
    \item \textcolor{blue}{Your specification of a utility function also has some ethical dimension, because that is how you choose what to do.}
        \begin{itemize}
            \item 
        \end{itemize}
    \item \textcolor{blue}{Life expectancy, success probability of treatment, cost of treatment,  and above all, availability of treatment, are all important factors to consider.}
        \begin{itemize}
            \item 
        \end{itemize}
    \item \textcolor{blue}{You can start off the project with a simple utility for the first deadline, and refine it later.}
        \begin{itemize}
            \item 
        \end{itemize}
    \item \textcolor{blue}{The project requires you to specify policies from the outset.}
        \begin{itemize}
            \item 
        \end{itemize}
    \item \textcolor{blue}{A policy can be generated easily once you have a predictive model, but you can leave policy optimisation and model tuning for the last part of the project.}
        \begin{itemize}
            \item 
        \end{itemize}
\end{itemize}